\chapter{Miscellaneous Results}
\section{Thompson like characterization}
{\bf Netto:}  Let $x,y \in S_n$ be selected randomly.  
$Pr[ \langle x,y \rangle =S_n]= {\frac 3 4}$.  
\\
\\
{\bf Thompson Order Formula:} Suppose $G$ has $s\geq 2$ classes of involutions, $C_1, \ldots , C_s$.
Put $d_{ijk} = |\{ (u,v): u \in C_i, v \in C_j, w=(uv)^m, w \in C_k \}|$.  Put $n_i = {\frac {|G|} {|C_i|}}$ then
$|G| = n_i n_j \sum_k d_{ijk} $. (Proved earlier)
\\
\\
{\bf Sample characterization of $S_5$:}
If $G$ is a finite group with two conjugacy classes of involutions ($ccl_1, ccl_2)$ having
centralizers, $C_1= C(u_1) = \langle u_1 \rangle \times S_3$ and
$C_2= C(u_2) = D_8$ then $G = S_5$.
\\
In $S_5$, $u_1= (12)$, $u_2= (12)(34)$.
\\
\\
1. $C_2 \in S_2(G)$.
\\
\\
2.  After conjugation, we can assume, $u_1 \in C_2, u_2 \in C_1$.
Let $x_1 \in ccl_1, x_2 \in ccl_2$ be involutions.  Let $S_i= \{ (u, v):
u \in x_1^G, v \in x_2^G, x_i \in \langle u, v \rangle \}$. Put $s_i = |S_i|$.
$|G|= s_1|C_G(x_2)| + s_2 |C_G(x_1)|$.
(In the real $G$, $|ccl_G(u_1)| = 10$ and $|ccl_G(u_2)|= 15$.)
Note that if $x \in x_1^G$ and $y \in x_2^G$, $|xy|$ is even (otherwise they would be
conjugate), $x,y \in C((xy)^{\frac {|xy|} 2})$.
\\
\\
3. 
$C_2 \cong D_8$ has three conjugacy classes of involutions.  
$D_8= \langle u, v \rangle $, $u^2=v^2=1$, $t= uv$ and $|t| = 4$.
$C_2= \langle (12),(14)(23) \rangle $, $t= (1324)$.
$u_2= (12)(34)$.
$ccl_{C_2}((14)(23))= \{ (14)(23), (13)(24) \}$,
$ccl_{C_2}((12))= \{ (12), (34) \}$,
$ccl_{C_2}((12)(34))= \{ (12)(34) \}$.  If $x \ne u_2$, $ x \sim x u_2$.
$G$ contains a non-cyclic group, $V$, of order $4$.
$V= ccl_{C_2}((14)(23)) \cup \{ 1 \} \cup ccl_{C_2}((12)(34))$.
Since $G$ has two classes of involutions, $s_2 = 0$ or $s_2 = 4$ and all the
involutions in $V$ are $G$-conjugate.
\\
\\
4.
$C_1$ has three conjugacy classes of involutions.  $x \ne u_1 \rightarrow x \nsim x u_1$.
$ \langle u_1 \rangle \times S_3$. 
$ccl_{C_1}((12))= \{ (12) \}$,
$ccl_{C_1}((12)(34))= \{ (12)(34), (12)(35), (12)(45), \}$,
$ccl_{C_1}((34))= \{ (34) , (35), (45) \}$.  If $x \ne u_1$, $ x \nsim x u_1$.
Since $G$ has two classes of involutions and for any $u_1 \ne x \in Inv(C_1 )$,
exactly one of $x$  or $xu_1$ is conjugate to $u_1$, $s_1 = 9$.
\\
\\
5.
$|G|= 9 \cdot 8 + 4 \cdot 12 = 120$, if $s_2=4$ or $|G|= 9 \cdot 8 = 72$, if $s_2 = 0$.
\\
\\
6. $|G| \ne 72$: If $|G|=72$, let
$P \in S_3(C_1)$, $P \subseteq Q \in S_3(G)$.  
$|Q|=9$ and $ \langle C_1 , Q \rangle \subseteq N(P)$,
$36 \mid |N(P)|$.
$\exists H: C(P) \subset H: |H|=36$.  $u_1 \in H$ and $u_2$ is a square in $H$.
$H \lhd G$ and $H$ contains all involutions in $G$ hence $C_2 \cap H$ contains all involutions of
$C_2$ but $|C_2 \cap H|=4$ and there are $5$ involutions in $C_2$.
\\
\\
7. By 3, $C_2$ has a normal four-group, $V$, with $u_2 \in V$ and all the involutions
in $V$ are $G$-conjugate.
Let $x \in G$ then $x^{-1} u_2 x \ne u_2$, $x^{-1} u_2 x \in V$ then
$x^{-1} C_2 x \ne C_2$ and
$u_2 \in C(x^{-1} u_2 x) = x^{-1} C_2 x$.
\\
\\
8. By 7, $N(V)$ contains at least two Sylow subgroups of $G$.
\\
\\
9.  $C(V)=V$.
$N(V)/V \cong S_3$ (permutes all $3$ involutions of $V$), by 7 above, and $|N(V)|= 24$.
\\
\\
10. $G:N(V)= 5$. Let $\phi: G \rightarrow \{N(V)x_i\}$ be the permutation representation
on the cosets of $N(V)$ in $G$.  $ker(\phi) = 1$ so $G \cong S_5$.
If $g \in G$ is an element
of order $5$, $g$ acts as a $5$-cycle on the cosets.  If $t$ is an element of order $2$,
it is of the form $(12)$ or $(12)(34)$.
\section{Isaac's treatment of central extensions}
{\bf Definition:} A central extension of $G$ is a pair $(\Gamma, \pi)$ with $\pi: \Gamma \rightarrow G$ and $ker(\pi) = {\mathbb Z}(\Gamma)$.
\\
\\
{\bf Theorem 1:}
Let $(\Gamma, \pi)$ be a central extension of $G$, $A=ker(\pi)$ and let $X= \{x_g| g \in G \}$ be coset representatives for $\Gamma/A$.
Define $\alpha$ by $x_g x_h = \alpha(g,h) x_{gh}$, then $\alpha \in Z(G,A)$ is well defined and the resulting multiplication is associative.
\begin{quote}
\emph{Proof:} Compute $x_g x_h x_k$ both ways and compare.  Put $y_g = \mu(g)x_g$ then
$y_g y_h = \mu(g) \mu(h) \mu(gh)^{-1} \alpha(g,h)$.
\end{quote}
{\bf Definition:} $A$ divisible if $\forall a \in A, n \in {\mathbb Z}^+, \exists b \in A: b^n=a$.  $M(G)= H(G, {\mathbb C}^{\times})$.
$\hat{A}$ is the set of linear characters of $A$.
\\
\\
{\bf Theorem 2:}
Let $A$ be abelian, $Q \subseteq A$, $Q$, divisible and $|A:Q| < \infty$ then $Q$ is complemented in $A$.
\begin{quote}
\emph{Proof:} By induction on $|A:Q|$.  True if $|A:Q|=1$.  Choose $a \in G \setminus A$. $n=|aQ|$ in $A/Q$.
$u = a^n$, $v \in Q: v^n=u$.  Put $b= av^{-1}$ and $\langle b \rangle \cap Q =1$.  ${\overline A}= A/\langle b \rangle$.
${\overline Q} = Q\langle b \rangle / \langle b \rangle$ and ${\overline Q} = Q$.  
$|{\overline A}:{\overline Q}| = |A:Q\langle b \rangle| < |A:Q|$, so ${\overline Q}$ is complemented by induction and 
$\exists B \subseteq A: B \cap Q\langle b \rangle = \langle b \rangle$ and $QB =A$.  $Q \cap B = Q \cap Q\langle b \rangle \cap B= $
$Q \cap \langle b \rangle = 1$.
\end{quote}
{\bf Theorem 3:}   If $F$ is algebraically closed and $G$ is finite, $|H(G,A)| \mid |G|$.
\begin{quote}
\emph{Proof:} 
Claim: $B(G, F^{\times})$ is divisible:
$B(G, F^{\times})$ is complemented in $Z(G, F^{\times})$.  For $\beta \in B(G, F^{\times})$, $\beta = \delta(\mu)$ for some
$\mu:G \rightarrow F^{\times}$.  Choose $\nu(g) \in F^{\times}: \nu(g)^n = \mu(g)$, we can do this since $F$ is algebraically closed.
$\delta(\nu)^n = \delta(\mu)= \beta$.  
We can apply previous lemma and once we show $|H(G, F^{\times})| < \infty$.\\
\\
For $\alpha \in Z(G, F^{\times})$, put
$\mu(g) = \prod_{x \in G} \alpha(g,x)$.
$\alpha(g, hx) \alpha(h, x) = \alpha(gh, x)\alpha(g, h)$ so
$\prod_{x \in G} \alpha(g, hx) \alpha(h, x) = \prod_{x \in G} \alpha(gh, x)\alpha(g, h)$ so
$\mu(g) \mu(h) = \mu(gh) \alpha(g, h)^{|G|}$.  $\alpha(g, h)^{|G|} \in B(G, F^{\times})$ and
$exp(H(G, F^{\times})) \mid |G|$.
Putting $U = \{ \alpha \in Z(G, F^{\times}): \alpha^{|G|} = 1 \}$ and $A = \langle B(G, F^{\times}), \alpha \rangle$.
$|A : B(G, F^{\times})| \mid |G|$.  By the previous result, $B(G, F^{\times})$ is complemented in $Z(G, F^{\times})$ so
$B(G, F^{\times})U = Z(G, F^{\times})$.   $\forall u \in U, u: G \times G \rightarrow \{y \in F: y^{|G|} = 1 \}$.
$|H(G, F^{\times})| = B(G, F^{\times})U:B(G, F^{\times})| \leq |U| < \infty$, and we can apply the previous result, proving the lemma.
\end{quote}
{\bf Definition:}  Choose a set of coset representatives in $\Gamma/A$, as before and $\pi(x_g) = g$.  Let
$\alpha \in Z(G, A)$, defined by $x_g x_h = \alpha(g,h) x_{gh}$.  For $\lambda \in \hat{A}$, define $\eta(\lambda) = {\overline {\lambda(\alpha)}}$.
$\lambda(\alpha)(g,h) = \lambda(\alpha(g,h))$.  Bar is the canonical map from $Z(G, {\mathbb C}^{\times})$ to $H(G, {\mathbb C}^{\times}) = M(G)$.
$\eta: \hat{A} \rightarrow M(G)$ is defined by that map, called the \emph{standard map}.
\\
\\
{\bf Theorem 4 (Schur):} Given $G$ and $A$, abelian, there is a central extension with $ker(\pi)=A= M(G)$
\begin{quote}
\emph{Proof:}
Let $M$ be a complement of $B(G, F^{\times})$ in $Z(G, F^{\times})$. Let $M = \hat{A}$.
Define $\alpha(g,h)$ by $\alpha(g, h)(\gamma) = \gamma(g,h), \gamma \in M$.  $\alpha(g,h) \in A$.
$\alpha(gh,k) \alpha(g,h) (\gamma) =  \gamma(gh, k) \gamma(g,h)$.  
Since $\gamma$ runs over factor sets, $\alpha \in Z(G, F^{\times})$.  Let $\Gamma, G, X$ be as in the earlier results.
$\lambda(\alpha(g,h))) = \alpha(g,h)(\gamma) = \gamma(g,h)$ and $\lambda(\alpha) = \gamma$.  
$|A| = |\hat{A}| \geq |\eta(\hat(A))| = |M(G)| = |A|$.
\end{quote}
\section{Other Results}
{\bf Theorem 5:}  Sylow subgroups of $\Phi(G)$ are normal in $G$.
\begin{quote}
\emph{Proof:} Frattini.
\end{quote}
{\bf Theorem 5a:}  If $G$ is simple and every subgroup of $G$ is Abelian.  If $M \ne N$ are maximal then
$M \cap N = 1$.
\begin{quote}
\emph{Proof:} If not, $G= \langle M, N \rangle  \subseteq C_G(M \cap N)$.
\end{quote}
{\bf Theorem 6:} If every proper subgroup of $G$ is nilpotent, $G$ is solvable.
\begin{quote}
\emph{Proof:} Let $G$ be a minimal counterexample.  $G$ is simple. Let $M, N$ be maximal with $M \cap N$
as large as possible. 
$N_G(M)= M$ and $N_G(N)= N$.
Since $M$, $N$ are nilpotent $N_M(M \cap N) > M \cap N$ and
$N_N(M \cap N) > M \cap N$.
The number of non-identity elements contained in conjugates of $M$ is at most $(|M| -1) \cdot |G:M|$.
$M \cap N = 1$.
Now apply 5a.
\end{quote}
{\bf Theorem 7:} $SL_2(4) \cong A_5$.
\begin{quote}
\emph{Proof:}
$|SL_2(4)|=60$ and $|A_5|=60$. and both are simple.  Let $G=SL_2(4)$. By Sylow, in $G$, $n_3 = 3$ or $n_3=5$.
Set $H=N_G(P), P \in S_2(G), n=n_3$. Let $\varphi: G \rightarrow S_n$ be the permutation representation on the
cosets of $H$.  If $n=3$, $Core_G(H) \ne 1$, since $5 \nmid |S_3|$.  So $n=n_3=5, |H|=12$ and 
$\varphi: G \rightarrow S_5$.  Since $Core_G(H) = 1$, $\varphi$ is an injection into $S_5$.  If the image contains
an odd permutation, the image of $\varphi$ has a subgroup of $A_5$ of order $30$ which must be normal in
$A_5$, a contradiction.
\end{quote}
{\bf Theorem 8:} $A_5$ is the symmetry group of the icosahedron.
\begin{quote}
\emph{Proof:} Let $O$ be the icosahedron and $G$ be its group of symmetries. 
$O$ has $12$ verticies and $20$ faces with $5$ edges incident on a vertex, so each vertex can go into
$12$ verticies and an adjacent vertex can go into one of $5$. This uniquely determines a symmetry, so
$|G|= 12 \cdot 5=60$.  Let $P \in S_5(G)$, $P$ permutes the verticies adjacent to a point.  Since
$G$ is transitive on verticies, $|G:G_a|=12$ (where $a$ is a vertex), so $G_a = P$ for some $P$.
$|G:N_G(P)|= 5$ and $|N_G(P)| = 12$.  Set $H=N_G(P)$ and let $\varphi: G \rightarrow S_5$ be a permutation
representation on the cosets of $H$.  Only the identity symmetry fixes all such $H$ so $\varphi$ is
an injection into $S_5$.  No symmetry swaps exactly two points so the image of $\varphi$ lies in $A_5$.
Thus $G \cong A_5$.
\end{quote}
{\bf Theorem 9:} Maximal subgroups of solvable groups have index $p^k$, some $p \in \pi(G)$.
\begin{quote}
\emph{Proof:}
Let $H$ be a minimal normal subgroup oog $G$. $H$ is elementary abelian so it has order $p^n$.
Let $M$ be a maximal subgroup.  If $H \subseteq M$, the theorem holds by induction.  If not
$G=HM$ and $G/H \cong M/M \cap H$.  So ${\frac {|G|} {|H|}} = {\frac {|M|}{|M \cap H|}}$ and
${frac {|G|} {|M|}} = {\frac {|H|} {M \cap H}}$ but $|H|$ is a prime power, so we're done.
\end{quote}
{\bf Theorem 10:} If $|P|= p^3$, $P' \ne 1$, then $\Phi(P) = {\mathbb Z}(P)$.  $P/\Phi(P) \cong {\mathbb Z}_p \times {\mathbb Z}_p$ and
has $p+1$ maximal subgroups.
\begin{quote}
\emph{Proof:}
\end{quote}
{\bf Theorem 11:} If $G$ has at least $2$ Sylow-$p$ subgroups, (a)$P,Q \in S_pp(G)$ are chosen with $|P \cap Q|$ maximal, $N_G(P \cap Q)$
is not a $p$-group, and (b) $N_G(P \cap Q)$ has at least two Sylow-$p$ subgroups.
\begin{quote}
\emph{Proof:}
\end{quote}
{\bf Theorem 12:} There is a unique simple group, $G$ if order $168= 2^3 \cdot 3 \cdot 7$.
\begin{quote}
\emph{Proof:}
\\
\\
{\bf Lemma 1:} $G$ has no proper subgroups of index $<7$.
\\
If it did and $H$ was such a subgroup, $G/Core_G(H)$ would be isomorphic to a subgroup of $S_6$, so there would be an
element of order $7$ in $Core_G(H)$, but $G$ is simple, contradiction.
\\
\\
{\bf Lemma 2:} If $S \in S_7(G)$, $n_7=|G:N_G(S)|=8$ so no $2$ element centralizes $S$.
\\
$n_7=8$, so $|N_G(S_7)|= 3 \cdot 7$.  No element of order $2$ normalized $S_7$ so there
is no element of order $14$ in $G$.
\\
{\bf Lemma 3:} $G$ has no element of order $21$.
\\
If there were an element of order $21$, $7 \mid N_G(S_3)$.
$n_3= 7$ or $n_3= 28$.  Suppose $n_3=7$ and
$P \in S_3(N_G(S_3)$ and
$T \in S_2(N_G(S_3)$.
$|N_G(S_3)|=24$. $S_3$ normalizes some $S_7$, say $R$. $P = P^t \subseteq N_G(R^t)$.
$T$ acts by conjugation on $S_7(G)$ and is transitive on the orbit. Hence $P$ normalizes
every Sylow $7$ subgroup of $G$ but this is a normal subgroup.
\\
\\
{\bf Lemma 4:} $R \in S_3(G)$,  $n_3=|G:N_G(R)|=28$ and $|N_G(S_3)| = 6$.
\\
By the above.
\\
\\
{\bf Lemma 5:} $V \subseteq G$, $V$ a Klein $4$-group with $N_G(V) \cong S_4$.
\\
Pick $T_1, T_2 \in S_2(G)$ with $V= T_1 \cap T_2$ as large as possible.
$V$ is a Klein group and $N_G(V)=S_4$.  Put $N=N_G(V)$.  $|V| = 2$ or
$|V| = 4$. $N$ acts on $V - \{1\}$.  If $7 \mid |N|$ a two element would
normalize a Sylow $7$ groups which is ruled out above.  By theorem 11(b),
$|N= 2^a \cdot 3$i, $a = 2$ or $a = 3$.  Let $P \in S_3(G)$, $N_N(P)$ has order
$3$ or $6$. So $N$ has four Sylow $3$ subgroups, all permuted transitively by $N$.
Groups of order $12$ have a normal Sylow $2$ or Sylow $3$ subgroup. $|N|=24$.
Let $K$ be the kernel of $N$ acting on the Sylow $3$ subgroups. If $K=1$,
$N \cong S_4$.  If $K > 1$, $K$ has an element of order dividing $6$ and $P$
is not contained in $K$.  So $|K|=2$. $N/k$ has order $12$, a contradiction.
\\
\\
{\bf Lemma 6:} If $Q \in S_2(G)$, $Q \cong D_8$.
\\
$S_4$ has a $D_8$ subgroup.
\\
\\
{\bf Lemma 7:} $N_G(R) \cong S_3$.
\\
No element of order $2$ commutes with an element of odd prime order. $T \cong D_8$ so
${\mathbb Z}(T)= \langle z \rangle$.  Since $C(z)$ has no elements of odd prime order,
$C(z)=T$.
\\
\\
{\bf Lemma 8:} If $T \in s_2(G)$, $n_2= |G:N_G(T)| = 21$. $G_G(T) = \langle z \rangle$ and ${\mathbb Z}(T) = \langle z \rangle$.
\\
$z$ has $21$ conjugates since $|C_G(z)|=8$ and (by 6), one conjugacy class of $4$ elements.  So,
there are $42$ elements of order $4$, $48$ elements of order $7$, and $56$ elements of order $3$.
\\
\\
{\bf Lemma 9:} $G$ has a unique conjugacy class of elements of order $2$.
\\
All $167$ non-identity elements are accounted for above, so every $2$ element is conjugate to $z$,
Now, $V \leq T$.  Let $W$ be the other Klein group in $T$.  $V$ and $W$ are not conjugate.
\\
\\
{\bf Lemma 10:} $N_G(W) \cong S_4$.
\\
Let $W = \langle z, w \rangle$.  $z^g=w$.  Put $T_0 = C_G(w)$.  i$W = T \cap T_0$ and
Lemma 5 gives the result.
\\
\\
{\bf Definition:} If 
$V_1, \ldots , V_7$ are the conjugates of $V$ in $G$ and
$W_1, \ldots , W_7$ are the conjugates of $W$ in $G$, call the $V_i$ points and the $W_i$ lines.
$V_i$ is on $W_i$ iff $V_i \subseteq W_i$.
\\
\\
{\bf Lemma 11:} Each line contains $3$ points.
\\
\\
{\bf Lemma 12:} Any $2$ points lie on exactly one line.
\\
\\
{\bf Lemma 13:} Each pair of lines intersect in exactly one point.
\\
\\
{\bf Conclusion:} $G$ is simple and $G \cong GL_3(2)$.
\end{quote}
{\bf Theorem 13:} If $G$ is simple and $|G|=p^2qr$, $G \cong A_5$.
\begin{quote}
\emph{Proof:}
\end{quote}
{\bf Theorem 14:} If $T \in S_2(G)$, $G = GL_3(4)$, then $T$ consists of upper triangular marticies.
\begin{quote}
\emph{Proof:}
Set
$A=
\left(
\begin{array} {ccc}
1 & a & b \\
0 & 1 & c \\
0 & 0 & 1 \\
\end{array}
\right)
$.
$A^2=
\left(
\begin{array} {ccc}
1 & 0 & ac \\
0 & 1 & c \\
0 & 0 & 1 \\
\end{array}
\right)
$ and
$A^4=
\left(
\begin{array} {ccc}
1 & 0 & 0 \\
0 & 1 & 0 \\
0 & 0 & 1 \\
\end{array}
\right)$. So the set of upper tringular matricies has order $|T|=4^3=2^6$ and  $T \in S_2(G)$.
There are $4^2=2^4$ involutions in $T$ and no element of $T$ has order greater than $4$.
\end{quote}
{\bf Theorem 15:} If $G = PSL_3(4)$, then $G$ has no element of order $15$ (In fact, the order of elements
of $G$ are $\leq 7$.)
\begin{quote}
\emph{Proof:}
The possible rational canonical forms for $A \in SL_3(4)$ are:
$A=
\left(
\begin{array} {ccc}
0 & 0 & a \\
1 & 0 & b \\
0 & 1 & c \\
\end{array}
\right)$,
$A=
\left(
\begin{array} {ccc}
a & 0 & 0 \\
0 & b & 0 \\
0 & 0 & c \\
\end{array}
\right)$,
and
$A=
\left(
\begin{array} {ccc}
a & 0 & 0 \\
0 & 0 & b \\
0 & 1 & c \\
\end{array}
\right)$.  The second form yields elements of order $1$ or $3$ with $abc=1$.
The third form must satisfy $ab=1$. The first form must satisfy $a=1$.  Except for order $3$,
this leaves:
$A=
\left(
\begin{array} {ccc}
0 & 0 & 1 \\
1 & 0 & b \\
0 & 1 & c \\
\end{array}
\right)$
or
$A=
\left(
\begin{array} {ccc}
b & 0 & 0 \\
0 & 0 & b^{-1} \\
0 & 1 & c \\
\end{array}
\right)$.
$A_5=
\left(
\begin{array} {ccc}
0 & 0 & 1 \\
1 & 0 & \alpha \\
0 & 1 & \alpha \\
\end{array}
\right)$, has order $5$ and
$A_7=
\left(
\begin{array} {ccc}
0 & 0 & 1 \\
1 & 0 & 1 \\
0 & 1 & 0 \\
\end{array}
\right)$, has order $7$.
$B_1=
\left(
\begin{array} {ccc}
b^2 & 0 & 0 \\
0 & b & 0 \\
0 & 0 & 1 \\
\end{array}
\right)$, and
$B_2=
\left(
\begin{array} {ccc}
1 & 0 & 0 \\
0 & 0 & 1 \\
0 & 1 & 1 \\
\end{array}
\right)$,  both have order $3$. $G$ has $10$ conjugacy classes with elements of order $1,2,3,4,5,7$.
$|C_G(\sigma_5)|=5$ ($2$ conjugacy classes),
$|C_G(\sigma_7)|=7$ ($2$ conjugacy classes).
\end{quote}
{\bf Theorem 16:} There are two non-isomorphic groups of order $20160= 2^6 \cdot 3^2 \cdot 5 \cdot 7$,
namely $A_8$  and $PSL_3(4)$.
\begin{quote}
\emph{Proof:}
$A_8$ has an element of order $15$, namely, $(123)(45678)$.  By Theorems 14 and 15, there
is no element of order $15$ in $G$ (In fact, the elements
of $PSL_3(4)$ have order $\leq 7$).
\end{quote}
{\bf Theorem 17:} $P \in S_P(G)$, $N_G(P) \subseteq M$, $M$, maximal, then $|G:M|=1 \jmod{p}$.
\begin{quote}
\emph{Proof:}
\end{quote}
{\bf Theorem 18:} If $p$ is the smallest prime dividing $|G|$, $P \in S_p(G)$ and $P$ is cyclic, $N_G(P)=C_G(P)$.
\begin{quote}
\emph{Proof:}
\end{quote}
{\bf Quasidihedral and generalized quaternion groups:}
$QD_{16} = \langle \sigma, \tau | \sigma^8=\tau^2=1, \tau \sigma \tau = \sigma^3 \rangle$.
$Q_{2^{n+1}} = \langle h, x | h^{2^n}= a = x^4, x^{-1} h x = h^{-1}, h^{2^{n-1}}= x^2 \rangle$.
